True versus apparent shapes of bow shocks

### 2018-02-28 papers/Papers1234/sec-conclusions.tex
Add 069-601 to the figure with images and circle fits

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/new-000-400-multi-fig}
  \caption[]{Example empirical determination of planitude and alatude
    for an observed bow shock.  Color scale and contours show an
    \textit{HST} H\(\alpha\) image (ACS F658N filter,
    \citealp{Bally:2006a}) of M42~000-400. Three different bows have
    been traced by hand on the image (red and white filled symbols):
    (\textit{a})~inner edge, (\textit{b})~ridge of maximum emission,
    and (\textit{c})~outer edge.  For each panel, the dark-colored
    circle shows the initial fit to the full set of points (white and
    red), using the algorithm described in
    Appendix~\ref{app:rcurv-empirical}.  The center of curvature and
    derived axis are shown by a small filled circle and dashed line in
    the same color. Lighter colored circles show three subsequent
    iterations where the fit is restricted to points within
    \(\pm \Delta\theta = \ang{75}\) of the axis.  The subset of points used in
    the final iteration is marked in red.  The perpendicular radii for
    the final iteration are shown by dotted lines. In panels
    \textit{a} and \textit{b} the iterations converge immediately, but
    in panel \textit{c} the iterations stably oscillate between two
    slightly different solutions. }
  \label{fig:000-400-fit}
\end{figure*}

\begin{figure}
  \includegraphics[width=\linewidth]{figs/000-400-planitude-alatude}
  \caption[]{Location in the projected planitude--alatude plane of the
    converged circle fits to the M42~000-400 bow.  For each solution,
    the two values of the alatude \(\Lambda'\), corresponding to
    \(R_{90}^+\) and \(R_{90}^-\), are joined by a vertical
    line. Large symbols show the results from the fits shown in
    Figure~\ref{fig:000-400-fit}, while small symbols show results for
    fits using \(\Delta\theta = \ang{60}\) instead of \ang{75}.}
  \label{fig:000-400-planitude-alatude}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{figs/000-400-Pi-vs-Dtheta}
  \caption[]{Sensitivity of fitted planitude to the parameter
    \(\Delta\theta\), which controls how close a point must be to the axis in
    order to be included in the circle fit. }
  \label{fig:000-400-Delta-theta}
\end{figure}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/new-two-arc-multi-fig}
  \caption[]{Example empirical determination of planitude and alatude
    for observed bow shocks associated with proplyds in the Orion
    Nebula.  Color scale and contours show an \textit{HST} H\(\alpha\)
    image (ACS F658N filter, \citealp{Bally:2006a}) of M42~000-400
    (panels \textit{a--c}) and M42~069-601 (panels \textit{d--f}). Three
    different bows have been traced by hand on the image (red and
    white filled symbols): (\textit{a, d})~inner edge, (\textit{b,
      e})~ridge of maximum emission, and (\textit{c, f})~outer edge.
    For each panel, the dark-colored circle shows the initial fit to
    the full set of points (white and red), using the algorithm
    described in Appendix~\ref{app:rcurv-empirical}.  The center of
    curvature and derived axis are shown by a small filled circle and
    dashed line in the same color. Lighter colored circles show three
    subsequent iterations where the fit is restricted to points within
    \(\pm \Delta\theta = \ang{75}\) of the axis.  The subset of points used in
    the final iteration is marked in red.  The perpendicular radii for
    the final iteration are shown by dotted lines. In panels
    \textit{a, b, d--f} the iterations converge immediately, but in
    panel \textit{c} the iterations stably oscillate between two
    slightly different solutions. }
  \label{fig:000-400-fit}
\end{figure*}

\begin{figure*}
  \begin{tabular}{p{0.45\linewidth} p{0.45\linewidth}}
    (a) & (b) \\
    \includegraphics[width=\linewidth]{figs/000-400-planitude-alatude}
    & \includegraphics[width=\linewidth]{figs/069-601-planitude-alatude}
  \end{tabular}
  \caption[]{Location in the projected planitude--alatude plane of the
    converged circle fits to the M42~000-400 bow.  For each solution,
    the two values of the alatude \(\Lambda'\), corresponding to
    \(R_{90}^+\) and \(R_{90}^-\), are joined by a vertical
    line. Large symbols show the results from the fits shown in
    Figure~\ref{fig:000-400-fit}, while small symbols show results for
    fits using \(\Delta\theta = \ang{60}\) instead of \ang{75}.}
  \label{fig:000-400-planitude-alatude}
\end{figure*}

\begin{figure*}
  \begin{tabular}{p{0.45\linewidth} p{0.45\linewidth}}
    (a) & (b) \\
    \includegraphics[width=\linewidth]{figs/000-400-Pi-vs-Dtheta}
    & \includegraphics[width=\linewidth]{figs/069-601-Pi-vs-Dtheta}
  \end{tabular}
  \caption[]{Sensitivity of fitted planitude to the parameter
    \(\Delta\theta\), which controls how close a point must be to the axis in
    order to be included in the circle fit. }
  \label{fig:000-400-Delta-theta}
\end{figure*}
